cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-03 paper-cardinalR.Rmd
Removed the code chunks

                             "n, hc, non_fac",
                             "n"),

@@

```{r branching-tb-pdf, eval=knitr::is_latex_output()}
branch_tb |>
  mutate(parm = paste0("\\texttt{", parm, "}")) |>
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR branching data generation functions", format="latex", col.names = c("Function", "Arguments", "Explanation"), escape = FALSE, booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "3.5cm") |>
  column_spec(2, width = "1.5cm") |>
  column_spec(3, width = "8cm")
```

@@

```{r data-gau, echo=TRUE}
gau <- gen_gaussian(n = 1000, p = 4, s = diag(4))
```

@@

```{r data-linear, echo=TRUE}
linear <- gen_longlinear(n = 1000, p = 4)
```

@@

```{r data-mobius, echo=TRUE}
mobius <- gen_mobius(n = 1000)
```

@@

```{r data-quadratic, echo=TRUE}
quadratic <- gen_quadratic(n = 1000)
```

@@

```{r data-cubic, echo=TRUE}
cubic <- gen_cubic(n = 1000)
```

@@

```{r data-pyrrect, echo=TRUE}
pyrrect <- gen_pyrrect(n = 1000, p = 4)
```

@@

```{r data-pyrtri, echo=TRUE}
pyrtri <- gen_pyrtri(n = 1000, p = 4)
```

@@

```{r data-pyrstar, echo=TRUE}
pyrstar <- gen_pyrstar(n = 1000, p = 4)
```

@@

```{r data-pyrholes, echo=TRUE}
pyrholes <- gen_pyrfrac(n = 1000, p = 4)
```

@@

```{r data-scurve, echo=TRUE}
scurve <- gen_scurve(n = 1000)
```

@@

```{r data-circle, echo=TRUE}
circle <- gen_circle(n = 1000, p = 4)
```

@@

```{r data-curvycycle, echo=TRUE}
curvycycle <- gen_curvycycle(n = 1000, p = 4)
```

@@

```{r data-unifsphere, echo=TRUE}
unifsphere <- gen_unifsphere(n = 1000, r = 1)
```

@@

```{r data-hollowsphere, echo=TRUE}
hollowsphere <- gen_hollowsphere(n = 1000, p = 4)
```

@@

```{r data-clusteredspheres, echo=TRUE}
clusteredspheres <- gen_clusteredspheres(n = c(1000, 100), k = 3, r = c(15, 3),
                                         loc = 10 / sqrt(3)) |>
  dplyr::select(-cluster)
```

@@

```{r data-swissroll, echo=TRUE}
swissroll <- gen_swissroll(n = 1000, w = c(-1, 1))
```

@@

```{r data-trefoil4d, echo=TRUE}
trefoil4d <- gen_trefoil4d(n = 500, steps = 5)
```

@@

```{r data-trefoil3d, echo=TRUE}
trefoil3d <- gen_trefoil3d(n = 500, steps = 5)
```

@@

```{r data-crescent, echo=TRUE}
crescent <- gen_crescent(n = 1000)
```

@@

```{r data-curvycylinder, echo=TRUE}
curvycylinder <- gen_curvycylinder(n = 1000, h = 10)
```

@@

```{r data-sphericalspiral, echo=TRUE}
sphericalspiral <- gen_sphericalspiral(n = 1000, spins = 1)
```

@@

```{r data-helicalspiral, echo=TRUE}
helicalspiral <- gen_helicalspiral(n = 1000)
```

@@

```{r data-conicspiral, echo=TRUE}
conicspiral <- gen_conicspiral(n = 1000, spins = 1)
```

@@

```{r data-nonlinear, echo=TRUE}
nonlinear <- gen_nonlinear(n = 1000, hc = 1, non_fac = 0.5)
```

>>>>

                             "n, hc, non_fac"),

@@

```{r branching-tb-pdf, eval=knitr::is_latex_output()}
branch_tb |>
  mutate(parm = paste0("\\texttt{", parm, "}")) |>
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR branching data generation functions", format="latex", col.names = c("Function", "Arguments", "Explanation"), escape = FALSE, booktabs = T, table.pos = "!ht", linesep = "")  |>
  column_spec(1, width = "3.5cm") |>
  column_spec(2, width = "1.5cm") |>
  column_spec(3, width = "8cm")
```

@@

```{r data-gau}
gau <- gen_gaussian(n = 1000, p = 4, s = diag(4))
```

@@

```{r data-linear}
linear <- gen_longlinear(n = 1000, p = 4)
```

@@

```{r data-mobius}
mobius <- gen_mobius(n = 1000)
```

@@

```{r data-quadratic}
quadratic <- gen_quadratic(n = 1000)
```

@@

```{r data-cubic}
cubic <- gen_cubic(n = 1000)
```

@@

```{r data-pyrrect}
pyrrect <- gen_pyrrect(n = 1000, p = 4)
```

@@

```{r data-pyrtri}
pyrtri <- gen_pyrtri(n = 1000, p = 4)
```

@@

```{r data-pyrstar}
pyrstar <- gen_pyrstar(n = 1000, p = 4)
```

@@

```{r data-pyrholes}
pyrholes <- gen_pyrfrac(n = 1000, p = 4)
```

@@

```{r data-scurve}
scurve <- gen_scurve(n = 1000)
```

@@

```{r data-circle}
circle <- gen_circle(n = 1000, p = 4)
```

@@

```{r data-curvycycle}
curvycycle <- gen_curvycycle(n = 1000, p = 4)
```

@@

```{r data-unifsphere}
unifsphere <- gen_unifsphere(n = 1000, r = 1)
```

@@

```{r data-hollowsphere}
hollowsphere <- gen_hollowsphere(n = 1000, p = 4)
```

@@

```{r data-clusteredspheres}
clusteredspheres <- gen_clusteredspheres(n = c(1000, 100), k = 3, r = c(15, 3),
                                         loc = 10 / sqrt(3)) |>
  dplyr::select(-cluster)
```

@@

```{r data-swissroll}
swissroll <- gen_swissroll(n = 1000, w = c(-1, 1))
```

@@

```{r data-trefoil4d}
trefoil4d <- gen_trefoil4d(n = 500, steps = 5)
```

@@

```{r data-trefoil3d}
trefoil3d <- gen_trefoil3d(n = 500, steps = 5)
```

@@

```{r data-crescent}
crescent <- gen_crescent(n = 1000)
```

@@

```{r data-curvycylinder}
curvycylinder <- gen_curvycylinder(n = 1000, h = 10)
```

@@

```{r data-sphericalspiral}
sphericalspiral <- gen_sphericalspiral(n = 1000, spins = 1)
```

@@

```{r data-helicalspiral}
helicalspiral <- gen_helicalspiral(n = 1000)
```

@@

```{r data-conicspiral}
conicspiral <- gen_conicspiral(n = 1000, spins = 1)
```

@@

```{r data-nonlinear}
nonlinear <- gen_nonlinear(n = 1000, hc = 1, non_fac = 0.5)
```

### 2025-12-03 paper-cardinalR.tex
Removed the code chunks

\caption{\label{tab:branching-tb-pdf}cardinalR branching data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Arguments & Explanation\\
\midrule
\texttt{gen\_expbranches} & \texttt{n, k} & Exponential shaped branches.\\
\texttt{gen\_linearbranches} & \texttt{n, k} & Linear shaped branches.\\
\texttt{gen\_curvybranches} & \texttt{n, k} & Curvy shaped branches.\\
\texttt{gen\_orglinearbranches} & \texttt{n, p, k} & Linear shaped branches originated in one point.\\
\texttt{gen\_orgcurvybranches} & \texttt{n, p, k} & Curvy shaped branches originated in one point.\\
\addlinespace
\texttt{gen\_cone} & \texttt{n, p, h, ratio} & Cone-shaped structure.\\
\texttt{gen\_gridcube} & \texttt{n, p} & Cube with specified grid points along each axes.\\
\texttt{gen\_unifcube} & \texttt{n, p} & Cube with uniform points.\\
\texttt{gen\_gaussian} & \texttt{n, p, s} & Multivariate Gaussian cloud.\\
\texttt{gen\_longlinear} & \texttt{n, p} & Long linear structure.\\
\addlinespace
\texttt{gen\_mobius} & \texttt{n} & Möbius strip in $3  ext{-}D$.\\
\texttt{gen\_quadratic} & \texttt{n} & Quadratic pattern in $2  ext{-}D$.\\
\texttt{gen\_cubic} & \texttt{n} & Cubic pattern in $2  ext{-}D$.\\
\texttt{gen\_pyrrect} & \texttt{n, p} & Rectangular-base, with a sharp or blunted apex.\\
\texttt{gen\_pyrtri} & \texttt{n, p} & Triangular-base, with a sharp or blunted apex.\\
\addlinespace
\texttt{gen\_pyrstar} & \texttt{n, p} & Star-shaped base, with a sharp or blunted apex.\\
\texttt{gen\_pyrfrac} & \texttt{n, p} & Pyramid with triangular pyramid-shaped holes.\\
\texttt{gen\_scurve} & \texttt{n} & S-curve in $3   ext{-}D$.\\
\texttt{gen\_circle} & \texttt{n, p} & Circle.\\
\texttt{gen\_curvycycle} & \texttt{n, p} & Curvy cell cycle.\\
\addlinespace
\texttt{gen\_unifsphere} & \texttt{n, r} & Uniform ball.\\
\texttt{gen\_hollowsphere} & \texttt{n, p} & Hollow sphere.\\
\texttt{gen\_gridedsphere} & \texttt{n, k, r, loc} & Grided sphere.\\
\texttt{gen\_clusteredspheres} & \texttt{n, w} & Multiple small spheres within a big sphere.\\
\texttt{gen\_hemisphere} & \texttt{n, steps} & Hemisphere.\\
\addlinespace
\texttt{gen\_swissroll} & \texttt{n, steps} & Swissroll structure.\\
\texttt{gen\_trefoil4d} & \texttt{n} & Trefoil in $4\text{-}D$.\\
\texttt{gen\_trefoil3d} & \texttt{n, h} & Trefoil in $3\text{-}D$.\\
\texttt{gen\_crescent} & \texttt{n, spins} & Crescent pattern.\\
\texttt{gen\_curvycylinder} & \texttt{n} & Curvy cylinder.\\
\addlinespace
\texttt{gen\_sphericalspiral} & \texttt{n, spins} & Spherical spiral.\\
\texttt{gen\_helicalspiral} & \texttt{n, hc, non\_fac} & Helical spiral.\\
\texttt{gen\_conicspiral} & \texttt{n} & Conic spiral.\\
\texttt{gen\_nonlinear} & \texttt{n} & Nonlinear hyperbola.\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{verbatim}
gau <- gen_gaussian(n = 1000, p = 4, s = diag(4))
\end{verbatim}

@@

\begin{verbatim}
linear <- gen_longlinear(n = 1000, p = 4)
\end{verbatim}

@@

\begin{verbatim}
mobius <- gen_mobius(n = 1000)
\end{verbatim}

@@

\begin{verbatim}
quadratic <- gen_quadratic(n = 1000)
\end{verbatim}

@@

\begin{verbatim}
cubic <- gen_cubic(n = 1000)
\end{verbatim}

@@

\begin{verbatim}
pyrrect <- gen_pyrrect(n = 1000, p = 4)
\end{verbatim}

@@

\begin{verbatim}
pyrtri <- gen_pyrtri(n = 1000, p = 4)
\end{verbatim}

@@

\begin{verbatim}
pyrstar <- gen_pyrstar(n = 1000, p = 4)
\end{verbatim}

@@

\begin{verbatim}
pyrholes <- gen_pyrfrac(n = 1000, p = 4)
\end{verbatim}

@@

\begin{verbatim}
scurve <- gen_scurve(n = 1000)
\end{verbatim}

@@

\begin{verbatim}
circle <- gen_circle(n = 1000, p = 4)
\end{verbatim}

@@

\begin{verbatim}
curvycycle <- gen_curvycycle(n = 1000, p = 4)
\end{verbatim}

@@

\begin{verbatim}
unifsphere <- gen_unifsphere(n = 1000, r = 1)
\end{verbatim}

@@

\begin{verbatim}
hollowsphere <- gen_hollowsphere(n = 1000, p = 4)
\end{verbatim}

@@

\begin{verbatim}
clusteredspheres <- gen_clusteredspheres(n = c(1000, 100), k = 3, r = c(15, 3),
                                         loc = 10 / sqrt(3)) |>
  dplyr::select(-cluster)
\end{verbatim}

@@

\begin{verbatim}
swissroll <- gen_swissroll(n = 1000, w = c(-1, 1))
\end{verbatim}

@@

\begin{verbatim}
trefoil4d <- gen_trefoil4d(n = 500, steps = 5)
\end{verbatim}

@@

\begin{verbatim}
trefoil3d <- gen_trefoil3d(n = 500, steps = 5)
\end{verbatim}

@@

\begin{verbatim}
crescent <- gen_crescent(n = 1000)
\end{verbatim}

@@

\begin{verbatim}
curvycylinder <- gen_curvycylinder(n = 1000, h = 10)
\end{verbatim}

@@

\begin{verbatim}
sphericalspiral <- gen_sphericalspiral(n = 1000, spins = 1)
\end{verbatim}

@@

\begin{verbatim}
helicalspiral <- gen_helicalspiral(n = 1000)
\end{verbatim}

@@

\begin{verbatim}
conicspiral <- gen_conicspiral(n = 1000, spins = 1)
\end{verbatim}

@@

\begin{verbatim}
nonlinear <- gen_nonlinear(n = 1000, hc = 1, non_fac = 0.5)
\end{verbatim}

>>>>

\caption{\label{tab:branching-tb-pdf}cardinalR branching data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3.5cm}>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Arguments & Explanation\\
\midrule
\texttt{gen\_expbranches} & \texttt{n, k} & Exponential shaped branches.\\
\texttt{gen\_linearbranches} & \texttt{n, k} & Linear shaped branches.\\
\texttt{gen\_curvybranches} & \texttt{n, k} & Curvy shaped branches.\\
\texttt{gen\_orglinearbranches} & \texttt{n, p, k} & Linear shaped branches originated in one point.\\
\texttt{gen\_orgcurvybranches} & \texttt{n, p, k} & Curvy shaped branches originated in one point.\\
\texttt{gen\_cone} & \texttt{n, p, h, ratio} & Cone-shaped structure.\\
\texttt{gen\_gridcube} & \texttt{n, p} & Cube with specified grid points along each axes.\\
\texttt{gen\_unifcube} & \texttt{n, p} & Cube with uniform points.\\
\texttt{gen\_gaussian} & \texttt{n, p, s} & Multivariate Gaussian cloud.\\
\texttt{gen\_longlinear} & \texttt{n, p} & Long linear structure.\\
\texttt{gen\_mobius} & \texttt{n} & Möbius strip in $3  ext{-}D$.\\
\texttt{gen\_quadratic} & \texttt{n} & Quadratic pattern in $2  ext{-}D$.\\
\texttt{gen\_cubic} & \texttt{n} & Cubic pattern in $2  ext{-}D$.\\
\texttt{gen\_pyrrect} & \texttt{n, p} & Rectangular-base, with a sharp or blunted apex.\\
\texttt{gen\_pyrtri} & \texttt{n, p} & Triangular-base, with a sharp or blunted apex.\\
\texttt{gen\_pyrstar} & \texttt{n, p} & Star-shaped base, with a sharp or blunted apex.\\
\texttt{gen\_pyrfrac} & \texttt{n, p} & Pyramid with triangular pyramid-shaped holes.\\
\texttt{gen\_scurve} & \texttt{n} & S-curve in $3   ext{-}D$.\\
\texttt{gen\_circle} & \texttt{n, p} & Circle.\\
\texttt{gen\_curvycycle} & \texttt{n, p} & Curvy cell cycle.\\
\texttt{gen\_unifsphere} & \texttt{n, r} & Uniform ball.\\
\texttt{gen\_hollowsphere} & \texttt{n, p} & Hollow sphere.\\
\texttt{gen\_gridedsphere} & \texttt{n} & Grided sphere.\\
\texttt{gen\_clusteredspheres} & \texttt{n, k, r, loc} & Multiple small spheres within a big sphere.\\
\texttt{gen\_hemisphere} & \texttt{n, p} & Hemisphere.\\
\texttt{gen\_swissroll} & \texttt{n, w} & Swissroll structure.\\
\texttt{gen\_trefoil4d} & \texttt{n, steps} & Trefoil in $4\text{-}D$.\\
\texttt{gen\_trefoil3d} & \texttt{n, steps} & Trefoil in $3\text{-}D$.\\
\texttt{gen\_crescent} & \texttt{n} & Crescent pattern.\\
\texttt{gen\_curvycylinder} & \texttt{n, h} & Curvy cylinder.\\
\texttt{gen\_sphericalspiral} & \texttt{n, spins} & Spherical spiral.\\
\texttt{gen\_helicalspiral} & \texttt{n} & Helical spiral.\\
\texttt{gen\_conicspiral} & \texttt{n, spins} & Conic spiral.\\
\texttt{gen\_nonlinear} & \texttt{n, hc, non\_fac} & Nonlinear hyperbola.\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@
